---
title: "Proposal"
---

# Motivation

FishEye International, a non-profit organization dedicated to combatting the scourge of illegal, unreported and unregulated (IUU) fishing, has been granted access to fishing-related companies' financial database, offered by an international finance corporation. Through their previous investigations, FishEye has discovered that companies with unusual arrangements are more likely to be engaged in IUU activities or other questionable practices. To leverage this valuable resource, FishEye has transformed the database into a comprehensive knowledge graph, which encompasses data on companies, owners, workers and revenue.

The primary objective of our project is to employ this graph to detect irregularities that may indicate a company's involvement in IUU fishing.

# Dataset

Dataset contains the knowledge graph with 27,622 nodes and 24,038 edges:

**Node Attributes:**

-   type -- Type of node as defined above.

-   country -- Country associated with the entity. This can be a full country or a two-letter country
    code.

-   product_services -- Description of product services that the \"id\" node does.

-   revenue_omu -- Operating revenue of the \"id\" node in Oceanus Monetary Units.

-   id -- Identifier of the node is also the name of the entry.

-   role -- The subset of the \"type\" node, not in every node attribute.

**Edge Attributes:**

-   type -- Type of the edge as defined above.

-   source -- ID of the source node.

-   target -- ID of the target node.

-   dataset -- Always \"MC3\".

-   role - The subset of the \"type\" node, not in every edge attribute.

# Related works

# Approach and Shiny App Prototype

### Question 1: Use visual analytics to identify anomalies in the business groups present in the knowledge graph.

### 

### Question 2: Develop a visual analytics process to find similar businesses and group them. This analysis should focus on a business\'s most important features and present those features clearly to the user.

### 

### Question 3: Measure similarity of businesses that you group in the previous question.

```{r}
pacman::p_load(jsonlite, tidyverse)

```

```{r}
MC3<-fromJSON('data/MC3.json')
```
